---
title: "Outputs - civil servants' survey"
subtitle: "version 2"
author: "Saar Alon-Barkat"
date: "`r Sys.time()`"
format:
  html:
    self-contained: true
    page-layout: full
    code-fold: true
    toc: true
    toc-location: left
execute:
  message: false
  warning: false
  cache: true
---

```{r hebrew setup}

Sys.setlocale("LC_ALL", "Hebrew")
```



```{r libraries}
library(tidyverse)
library(haven)
library(ggplot2)
library(reshape2)
library(ggthemes)
library(dplyr)
library(qualtRics)
library(tidyr)
library(stringr)
library(gridExtra)
library(scales)
library(gtsummary)
library(psy)
library(labelled)
library(rtlr)
library(multilevel)
library(mediation)
library(lavaan)
library(semhelpinghands)
library(semPlot)

set.seed(2023)
```

```{r}
#source("Operationalization_31.7.R")


```


# Descriptive


duration
```{r}
new_data %>% 
  filter((ranking !="junior") %>% replace_na(TRUE)) %>% 
  filter(INTENT_EXIT_2>0|
          PROJECT_EFFORT>0|
           PROJECT_VOICE>0) %>% 
  dplyr::select(Duration__in_seconds_) %>%  
  summary()

618/60


```





## Table 1 - Characteristics of survey sample and research population
```{r}
data_for_analysis_senior %>% data_frame()%>%
  dplyr::select(tenure,
         position_type,
         ranking,
         gender,
         age,
         education,
         religiosity,
         jurist)  %>%
  gtsummary::tbl_summary()
```

## CFA - Measurement model

one factor model 
- Indepandant variables: 
PAST_INFLUENCE = "Q4_1", "Q4_2", "Q4_3"
PAST_POLITICIZATION = "Q10_1", "Q10_2", "Q10_3"
PAST_EFFORT = "Q19"
PAST_VOICE ="Q22_1", "Q22_2", "Q22_3"
BACKSLIDING_2 =  "Q15_rescale", "Q16_1", "Q16_2", "Q16_3","Q16_4","Q16_5"
PROJECT_POLITICIZATION = "Q_11"
PROJECT_INFLUENCE = "Q_5"



1-factor model
```{r}
cfa.model.1factor <-
  'one_factor =~ Q4_1+ Q4_2+ Q4_3 + Q10_1+ Q10_2+ Q10_3 + PAST_EFFORT + Q22_1+ Q22_2+ Q22_3 + Q15+ Q16_1+ Q16_2+ Q16_3+ Q16_4+ Q16_5 + PROJECT_POLITICIZATION + PROJECT_INFLUENCE'

fit.cfa.model.1factor <- cfa(cfa.model.1factor,# model formula,
                             data = data_for_analysis_senior,
                             se = "robust",
                             std.lv = T)

summary(fit.cfa.model.1factor, fit.measures = TRUE, standardize = TRUE)
```


7-factor model (Table B1)
```{r}
cfa.model.7factor <-
  'past_influence =~ Q4_1+ Q4_2+ Q4_3 
   past_politicization =~ Q10_1+ Q10_2+ Q10_3
   past_effort =~ PAST_EFFORT
   past_voice =~ Q22_1+ Q22_2+ Q22_3
   backsliding_2=~ Q16_1+ Q16_2+ Q16_3+ Q16_4+ Q16_5 + Q15
   project_politicization =~ PROJECT_POLITICIZATION
   project_influence =~ PROJECT_INFLUENCE'

fit.cfa.model.7factor <- cfa(cfa.model.7factor,# model formula,
                             data = data_for_analysis_senior,
                             se = "robust",
                             std.lv = T)

summary(fit.cfa.model.7factor, fit.measures = TRUE, standardize = TRUE)
```

```{r}
anova(fit.cfa.model.7factor,fit.cfa.model.1factor)
```



## Table 2: descriptive statistics

```{r}
t1 <- data_for_analysis_senior %>% 
  dplyr::select(
                PAST_INFLUENCE,
                PAST_POLITICIZATION,
                PAST_EFFORT,
                PAST_VOICE,
                BACKSLIDING_2,
                PROJECT_POLITICIZATION,
                PROJECT_INFLUENCE) %>% 

  pivot_longer(cols = PAST_INFLUENCE:PROJECT_INFLUENCE) %>% 
  drop_na(value) %>% 
  mutate(name = name %>% car::recode("'BACKSLIDING_2' = '1. Perceived democratic backsliding';
      'PROJECT_POLITICIZATION' = '2. Expected politicization';  
      'PROJECT_INFLUENCE' = '3. Expected influence'; 
      'PAST_POLITICIZATION' = '4. Past politicization';
      'PAST_INFLUENCE' = '5. Past influence';
      'PAST_VOICE' = '6. Past voice';
      'PAST_EFFORT' = '7. Past work effort'"))

t1 %>%   group_by(name) %>% 
  dplyr::summarise(n = n(),
            Median = median(value,na.rm = T) %>% round(3),
            Mean = mean(value,na.rm = T) %>% round(3),
            SD = sd(value,na.rm = T) %>% round(3)) %>% 
    kableExtra::kable() %>% 
    kableExtra::kable_styling(bootstrap_options = c("condensed"),
                full_width = F,
                position = "left")
```


correlations between IVs
```{r}

data_for_analysis_senior %>% 
  dplyr::select(
                BACKSLIDING_2,
                PROJECT_POLITICIZATION,
                PROJECT_INFLUENCE,
                PAST_POLITICIZATION,
                PAST_INFLUENCE,
                PAST_VOICE,
                PAST_EFFORT) %>% 
  sjPlot::tab_corr(triangle = "lower",
                   #show.p = FALSE,
                   fade.ns = FALSE,
                   var.labels = str_c("(",1:7,")"))
```



## Figure 1


## Figure 2


# Main models

## OLS - no controls

Model for expected politicization & influence

```{r}
predictor_labels <- c(
  "BACKSLIDING_2" = "Democratic backsliding",
  "PAST_POLITICIZATION" = "Past politicization",
  "PAST_INFLUENCE" = "Past influence",
  "PROJECT_POLITICIZATION" = "Expected politicization",
  "PROJECT_INFLUENCE" = "Expected influence",
  "PAST_VOICE" = "Past voice",
  "PAST_EFFORT" = "Past work effort"
)
```


```{r}
politicization_mod1 <- lm(PROJECT_POLITICIZATION ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
            data=data_for_analysis_senior)

influence_mod1 <- politicization_mod1 %>%  update(PROJECT_INFLUENCE~.)

sjPlot::tab_model(politicization_mod1,influence_mod1,
                  show.est = F,
                  show.ci = F,
                  show.se = F,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                  dv.labels = c("Expected politicization","Expected influence"),
                  order.terms = c(2:4,1))

```



```{r}
#regression outputs with CIs
sjPlot::tab_model(politicization_mod1,influence_mod1,
                  show.std=T
)
```

Model for exit, voice and work
```{r}
exit_mod1 <- lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
            data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))

exit_mod2 <- exit_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)

voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE)
voice_mod2 <- voice_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)

work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT)
work_mod2 <- work_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)

sjPlot::tab_model(exit_mod1,exit_mod2,
                  voice_mod1,voice_mod2,
                  work_mod1,work_mod2,
                  show.est = F,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                  dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
                  order.terms = c(2,5:6,3:4,7:8,1))



```

```{r}
#regression outputs with CIs
sjPlot::tab_model(exit_mod1,exit_mod2,
                  voice_mod1,voice_mod2,
                  work_mod1,work_mod2,
                  show.std=T
)
```




## SEM models 



```{r}
SEM_All <-'
##latent variables##
Past_influence=~ Q4_1 + Q4_2 + Q4_3
Past_politicization=~ Q10_1 + Q10_2 + Q10_3
Demo_backsliding=~ Q16_1 + Q16_2 + Q16_3 + Q16_4 + Q16_5 + Q15
Past_voice=~Q22_1+Q22_2+Q22_3
Past_effort=~PAST_EFFORT

##Direct effects##
INTENT_EXIT_2 ~ cp_ex*Demo_backsliding
PROJECT_VOICE ~ cp_vc*Demo_backsliding + Past_voice
PROJECT_EFFORT ~ cp_eff*Demo_backsliding + Past_effort

##Mediators##
PROJECT_POLITICIZATION ~ a1*Demo_backsliding + Past_politicization 
PROJECT_INFLUENCE ~ a2*Demo_backsliding + Past_influence

INTENT_EXIT_2 ~ b1_ex*PROJECT_POLITICIZATION + Past_politicization
INTENT_EXIT_2 ~ b2_ex*PROJECT_INFLUENCE + Past_influence

PROJECT_VOICE ~ b1_vc*PROJECT_POLITICIZATION + Past_politicization
PROJECT_VOICE ~ b2_vc*PROJECT_INFLUENCE + Past_influence

PROJECT_EFFORT ~ b1_eff*PROJECT_POLITICIZATION + Past_politicization
PROJECT_EFFORT ~ b2_eff*PROJECT_INFLUENCE + Past_influence

## Indirect effects ##
tot_ind_exit := abs(a1*b1_ex) + abs(a2*b2_ex)
tot_ind_voice := abs(a1*b1_vc) + abs(a2*b2_vc)
tot_ind_effort := abs(a1*b1_eff) + abs(a2*b2_eff)

dir_backs_polit := a1
dir_backs_inf := a2

dir_backs_exit := cp_ex
dir_polit_exit := b1_ex
dir_infl_exit := b2_ex

dir_backs_voice := cp_vc
dir_polit_voice := b1_vc
dir_infl_voice := b2_vc

dir_backs_effort := cp_eff
dir_proj_polit_effort := b1_eff
dir_proj_infl_effort := b2_eff

##indirect effects##
ind_back_polit_exit := a1*b1_ex
ind_back_infl_exit := a2*b2_ex

ind_back_polit_voice := a1*b1_vc
ind_back_infl_voice := a2*b2_vc

ind_back_polit_effort := a1*b1_eff
ind_back_infl_effort := a2*b2_eff

##total effects##
tot_back_exit := cp_ex + (a1*b1_ex) + (a2*b2_ex)
tot_back_voice := cp_vc + (a1*b1_vc) + (a2*b2_vc)
tot_back_effort := cp_eff + (a1*b1_eff) + (a2*b2_eff)


##Correlations between mediators##
PROJECT_POLITICIZATION~~PROJECT_INFLUENCE

##Other correlations##
PROJECT_POLITICIZATION~~Past_influence
PROJECT_INFLUENCE~~Past_politicization
Past_politicization~~Past_influence
Past_effort~~PROJECT_POLITICIZATION
Past_effort~~PROJECT_INFLUENCE


##Contrasts
c1v2_exit := (a1*b1_ex) - (a2*b2_ex)
c1v2_voice := (a1*b1_vc) - (a2*b2_vc)
c1v2_effort := (a1*b1_eff) - (a2*b2_eff)'


fit_all <- sem(SEM_All, # model formula
                se = "bootstrap",
                missing="ML",
                data = data_for_analysis_senior)# 
```



```{r}
summary(fit_all, fit.measures=TRUE, standardized=TRUE)
```

```{r}
standardizedSolution_boot_ci(fit_all) %>% 
  filter(op==":=") %>% 
  dplyr::select(label,est.std,boot.ci.lower,boot.ci.upper,pvalue) %>% 
  mutate(across(2:4, round, 2)) %>% 
  mutate(across(5, round, 3)) %>% 
  gt::gt()
```


```{r}
parameterEstimates(fit_all, boot.ci.type	="basic", standardized = T, output = "text")
```

```{r}
fitmeasures(fit_all, c('chisq','df','pvalue','cfi','tli', 'rmsea', 'rmsea.ci.upper','rmsea.ci.lower', 'srmr')) %>% 
  broom::tidy() %>% 
  pivot_wider(names_from = names,values_from = x) %>% 
  mutate(chisq_01 = str_c(chisq %>% round(3)," [","df=",df,", p=",pvalue %>% round(3),"]"),
         rmsea_01 = str_c(rmsea %>% round(3)," CI[", rmsea.ci.lower %>% round(3),",",rmsea.ci.upper %>% round(3),"]"),
         cfi = cfi %>% round(3),
         tli = tli %>% round(3),
         srmr = srmr %>% round(3),
         n = fit_all@SampleStats@nobs) %>%
  dplyr::select('N' = n,
          'Chi-sq' = chisq_01,
         'CFI' = cfi,
         'TLI' = tli,
         'RMSEA' = rmsea_01,
         'SRMR' = srmr) %>% 
  t() %>% 
  kableExtra::kable()
```



# Online appendix

## Causal mediation analysis

Exit

```{r}
# Load necessary package
library(mediation)
set.seed(2023)

t1 <- data_for_analysis_senior %>% 
  drop_na(BACKSLIDING_2,INTENT_EXIT_2,PROJECT_VOICE,PROJECT_EFFORT,PROJECT_POLITICIZATION,PROJECT_INFLUENCE)


# Mediator 1 model
med1_model <- lm(PROJECT_POLITICIZATION ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
            data=t1)

# Mediator 2 model
med2_model <- lm(PROJECT_INFLUENCE ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
            data=t1)

# Outcome model med 1
outcome_model_1 <-
  lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE +
            PROJECT_POLITICIZATION,
            data=t1)


# Outcome model med 2
outcome_model_2 <-
  lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE +
            PROJECT_INFLUENCE,
            data=t1)


# Mediation analysis for the first mediator with bootstrapping
mediation_result_exit_politicization <-
  mediate(
    med1_model,
    outcome_model_1,
    treat = "BACKSLIDING_2",
    mediator = "PROJECT_POLITICIZATION",
    boot = TRUE,
    sims = 1000
  )

# Mediation analysis for the second mediator with bootstrapping
mediation_result_exit_influence <-
  mediate(
    med2_model,
    outcome_model_2,
    treat = "BACKSLIDING_2",
    mediator = "PROJECT_INFLUENCE",
    boot = TRUE,
    sims = 1000
  )

# Summary of the results
```

```{r}
summary(mediation_result_exit_politicization) 
```


```{r}
summary(mediation_result_exit_influence)
```


Voice

```{r}

# Outcome model med 1
outcome_model_1 <-
  lm(PROJECT_VOICE ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE +
            PROJECT_POLITICIZATION,
            data=t1)


# Outcome model med 2
outcome_model_2 <-
  lm(PROJECT_VOICE ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE +
            PROJECT_INFLUENCE,
            data=t1)


# Mediation analysis for the first mediator with bootstrapping
mediation_result_voice_politicization <-
  mediate(
    med1_model,
    outcome_model_1,
    treat = "BACKSLIDING_2",
    mediator = "PROJECT_POLITICIZATION",
    boot = TRUE,
    sims = 1000
  )

# Mediation analysis for the second mediator with bootstrapping
mediation_result_voice_influence <-
  mediate(
    med2_model,
    outcome_model_2,
    treat = "BACKSLIDING_2",
    mediator = "PROJECT_INFLUENCE",
    boot = TRUE,
    sims = 1000
  )

# Summary of the results
```

```{r}
summary(mediation_result_voice_politicization)
```


```{r}
summary(mediation_result_voice_influence)
```



Effort

```{r}

# Outcome model med 1
outcome_model_1 <-
  lm(PROJECT_EFFORT ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE + PAST_EFFORT + 
            PROJECT_POLITICIZATION,
            data=t1)


# Outcome model med 2
outcome_model_2 <-
  lm(PROJECT_EFFORT ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE + PAST_EFFORT + 
            PROJECT_INFLUENCE,
            data=t1)


# Mediation analysis for the first mediator with bootstrapping
mediation_result_work_politicization <-
  mediate(
    med1_model,
    outcome_model_1,
    treat = "BACKSLIDING_2",
    mediator = "PROJECT_POLITICIZATION",
    boot = TRUE,
    sims = 1000
  )

# Mediation analysis for the second mediator with bootstrapping
mediation_result_work_influence <-
  mediate(
    med2_model,
    outcome_model_2,
    treat = "BACKSLIDING_2",
    mediator = "PROJECT_INFLUENCE",
    boot = TRUE,
    sims = 1000
  )

# Summary of the results
```

```{r}
summary(mediation_result_work_politicization)
```


```{r}
summary(mediation_result_work_influence)
```

## Descripive illustration

```{r}
t1 <- data_for_analysis_senior %>% 
  mutate(high_backsliding = case_when(
    BACKSLIDING_2>0.84 ~ 1,
    BACKSLIDING_2<=0.84 ~ 0
  ),
  high_exit = case_when(
    INTENT_EXIT_2>0.5 ~ 1,
    INTENT_EXIT_2<=0.5 ~ 0
  ),
  low_voice = case_when(
    PROJECT_VOICE<0.5 ~ 1,
    PROJECT_VOICE>=0.5 ~ 0
  ),
  low_effort = case_when(
    PROJECT_EFFORT<0.5 ~ 1,
    PROJECT_EFFORT>=0.5 ~ 0
  ),
  
  )

t1 %>% count(PROJECT_EFFORT,low_effort)

t1 %>% 
  group_by(high_backsliding) %>% 
  summarise(mean(high_exit,na.rm=T),
            mean(low_voice,na.rm=T),
            mean(low_effort,na.rm=T))


#exit
0.3558282/0.1988950

#voice
0.2760736/0.1739130

#work effort
0.2787879/0.1746032
```






## Exit 1

```{r}
data_for_analysis_senior %>% count(INTENT_EXIT_1)
```
```{r}
data_for_analysis_senior %>%
  mutate(INTENT_EXIT_1_lab = case_when(
    INTENT_EXIT_1==0 ~ "1. ...to leave government as soon as possible",
    INTENT_EXIT_1==0.25 ~ "2. ...to leave government during the coming year",
    INTENT_EXIT_1==0.5 ~ "3. ...to stay in government, a least for the next two years",
    INTENT_EXIT_1==0.75 ~ "4. ...to stay in government, at least for the next five years",
    INTENT_EXIT_1==1 ~ "5. ...to stay in government for the rest of my career",
    
  )) %>%  
  dplyr::select(INTENT_EXIT_1_lab) %>% 
  tbl_summary()
```


```{r}

t1<- data_for_analysis_senior %>%
  mutate(INTENT_EXIT_1_lab = case_when(
    INTENT_EXIT_1==0 ~ "1. ...leave government as soon as possible",
    INTENT_EXIT_1==0.25 ~ "2. ...leave government during the coming year",
    INTENT_EXIT_1==0.5 ~ "3. ...stay in government, a least for the next two years",
    INTENT_EXIT_1==0.75 ~ "4. ...stay in government, at least for the next five years",
    INTENT_EXIT_1==1 ~ "5. ...stay in government for the rest of my career",
    
  )) %>%  
  drop_na(INTENT_EXIT_1_lab) %>% 
  group_by(INTENT_EXIT_1_lab) %>%
  summarize(n=n())%>%
mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))

t1%>% 
  #drop_na(trust_in_gov_lab)%>%
  ggplot(aes(x=factor(INTENT_EXIT_1_lab),y=n))+
  geom_col(alpha=0.8,fill="lightblue")+
  geom_text(aes(label=freq.lab),colour="gray20",size=3)+
  labs(title="",x="",y="Frequency")+
  #facet_wrap(vars(name),ncol = 3)+
  coord_cartesian(ylim = c(0,0.5))+
  coord_flip()  +
  theme_classic() 
```

```{r}
data_for_analysis_senior %>% 
    mutate(INTENT_EXIT_1_lab = case_when(
    INTENT_EXIT_1==0 ~ "1. ...leave government as soon as possible",
    INTENT_EXIT_1==0.25 ~ "2. ...leave government during the coming year",
    INTENT_EXIT_1==0.5 ~ "3. ...stay in government, a least for the next two years",
    INTENT_EXIT_1==0.75 ~ "4. ...stay in government, at least for the next five years",
    INTENT_EXIT_1==1 ~ "5. ...stay in government for the rest of my career",
    
  )) %>%  
  ggplot(aes(x=factor(INTENT_EXIT_1_lab),y=INTENT_EXIT_2))+
  #geom_boxplot()#+
  stat_summary(
    fun.y = mean,
    geom = "point",
    alpha = 0.5,
    size = 2
  ) +
    stat_summary(
    fun.data = mean_cl_normal,
    geom = "errorbar",
    fun.args = list(conf.int = 0.95),
    alpha = 0.5,
    width = 0.1,
    size = 1) +
     coord_flip()+
  labs(title="",x="Exit intention (first measure)",y="Exit intention (second measure)",fill="")+
  #facet_wrap(vars(wave))+
  theme_classic() 
```
```{r}
data_for_analysis_senior %>% remove_labels() %>% 
  dplyr::select(INTENT_EXIT_1,
                INTENT_EXIT_2,
                BACKSLIDING_2, 
                PROJECT_VOICE,
                PROJECT_EFFORT,
                PROJECT_POLITICIZATION,
                PROJECT_INFLUENCE,
                PAST_POLITICIZATION,
                PAST_INFLUENCE) %>% 
  sjPlot::tab_corr(triangle = "lower",
                   show.p = FALSE,
                   fade.ns = FALSE)
```



```{r}
exit_mod1 <- lm(INTENT_EXIT_1 ~ 
            BACKSLIDING_2,
            data=data_for_analysis_senior)

exit_mod2 <- exit_mod1 %>% update(.~.+ PROJECT_POLITICIZATION + PROJECT_INFLUENCE) 

exit_mod3 <- exit_mod1 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)

exit_mod4 <- exit_mod2 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)



#Table A8
sjPlot::tab_model(exit_mod1,exit_mod2,
                  exit_mod3,exit_mod4,
                  show.ci = F,
                  show.se = T,
                  collapse.se = T,
                  terms = c("(Intercept)",
                            "BACKSLIDING_2",
                            "PROJECT_POLITICIZATION",
                            "PROJECT_INFLUENCE"))

```



```{r}
exit_mod1 <- lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2,
            data=data_for_analysis_senior)

exit_mod2 <- exit_mod1 %>% update(.~.+ PROJECT_POLITICIZATION + PROJECT_INFLUENCE) 

exit_mod3 <- exit_mod1 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)

exit_mod4 <- exit_mod2 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)



#Table A8
sjPlot::tab_model(exit_mod1,exit_mod2,
                  exit_mod3,exit_mod4,
                  show.ci = F,
                  show.se = T,
                  collapse.se = T,
                  terms = c("(Intercept)",
                            "BACKSLIDING_2",
                            "PROJECT_POLITICIZATION",
                            "PROJECT_INFLUENCE"))

```


## Controls

Model for expected politicization & influence

```{r}
predictor_labels <- c(
  "BACKSLIDING_2" = "Democratic backsliding",
  "PAST_POLITICIZATION" = "Past politicization",
  "PAST_INFLUENCE" = "Past influence",
  "PROJECT_POLITICIZATION" = "Expected politicization",
  "PROJECT_INFLUENCE" = "Expected influence",
  "PAST_VOICE" = "Past voice",
  "PAST_EFFORT" = "Past work effort"
)
```


```{r}
politicization_mod1 <- lm(PROJECT_POLITICIZATION ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party,
            data=data_for_analysis_senior)
politicization_mod1_relig <- politicization_mod1 %>% update(.~.+religiosity)


influence_mod1 <- politicization_mod1 %>%  update(PROJECT_INFLUENCE~.)
influence_mod1_relig <- influence_mod1 %>% update(.~.+religiosity)

sjPlot::tab_model(politicization_mod1,politicization_mod1_relig,
                  influence_mod1,influence_mod1_relig,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels)#,
                  dv.labels = c("Expected politicization","Expected influence")

```


Model for exit, voice and work
```{r}
exit_mod1 <- lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2 +   
              PAST_POLITICIZATION + PAST_INFLUENCE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party,
            data=data_for_analysis_senior)
exit_mod1_relig <- exit_mod1 %>% update(.~.+religiosity)


voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist + ministry_by_party)
voice_mod1_relig <- voice_mod1 %>% update(.~.+religiosity)


work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT+ education+ gender +tenure+ position_type+ ranking+ age+ jurist + ministry_by_party)
work_mod1_relig <- work_mod1 %>% update(.~.+religiosity)


sjPlot::tab_model(exit_mod1,exit_mod1_relig,
                  voice_mod1,voice_mod1_relig,
                  work_mod1,work_mod1_relig,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                  dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2))



```



```{r, fig.width=8,fig.height=6}
p1<- cars %>% ggplot(aes(x=speed))+ geom_histogram()

p1

#ggsave("p1.jpg",width = 8, height = 4,dpi=600)
```

